\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage[pdftex, colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{caption}
\usepackage{atbegshi}
\usepackage{lscape}
\usepackage{caption}
\usepackage[multiple]{footmisc}
\usepackage[title]{appendix}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{adjustbox}
\usepackage{soul}
\usepackage{arydshln}
\usepackage{threeparttable}

\pagestyle{fancy}
\lhead{Eduard Storm}
\rhead{Instructor Evaluations, Department of Economics, UWM}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\linespread{1.3}

\setlength{\parindent}{0em}
\setlength{\parskip}{0em}


\begin{document}

\textbf{\large{Select Comments from Students on Teaching Performance}}\\

\textbf{Principles of Macroeconomics}

Uses a lot of examples in lecture rather than just telling us information \\

Funny guy that tries to make connections with the world and make what could be a mundane course interesting \\

The fact that the explanation/lecturing has a lot of examples and that makes it a lot easier to understand the material applied in real-life/ more practical situations \\

Eduard was very helpful when and responsive when asked questions about course material. He was a great leader and I liked his style of teaching; it was always easy to listen to him unlike my microecon professor. Furthermore, I liked the classic style of the course, where Eduard used the whiteboard
to write notes vs. using a powerpoint. This reinforced students to actually have to take notes and listen to Eduard's lectures. I overall enjoyed the class and learned a great deal. \\

Professor Storm is a very likable and capable instructor who manages to make a not too interesting topic quite engaging. His class structure is efficient and his grading is fair. Overall, he is a fantastic professor and a very personable guy \\

Eduard is a terrific instructor, charismatic and highly attentive. He's an asset to the university \\

Eduard was extremely engaging and helpful and made learning econ very enjoyable. Thanks Eduard!! \\

He went into detail about every lesson and provided real life examples. It was interesting to see how this class ties into real life and how it influences everything around us. He was very effective in his teaching methods. \\

One of the best instructors I've ever had. \\

Eduard is a great professor as he has great examples and is able to explain everything he does in class and encourages questions. Exams and homework are great together and result in great performances on exams. Really good dude! \\

His fun bubbly personality makes it so much fun to go to class. He has a lot of real world applications that help \\

I really appreciated the way Eduard tried to make class fun and entertaining. He was also very helpful when giving real life examples and explaining the material. I felt much more confident in Eduards class than my previous Econ lecture from last year. \\

The instructor's strengths is explaining things in detail. I understand things I once thought were complicated.  \\

The course is very laid-back and teaches the content based on a conceptual understanding vs making sure we read a textbook. 

I like that this is a pretty laid back class, but I'm still learning a lot. I also love the humor and real-world scenarios brought into class everyday.  \\

I enjoy Eduard's personality and his use of relatable examples to help us grasp the material. He explains things thoroughly.  \\

Very knowledgeable. Extremely kind. Respects his students greatly. Really I'm quite impressed by his ability to be humorous and maintain control over the class.  \\

He is an awesome instructor that keeps me engaged more than other classes. The class opens up my curiosity to the real world and different ideas that are occurring all around us today. You are an awesome teacher that gets everyone involved and keeps people engaged.  \\

Very good teaching style, one of my favorite professors in college so far. Very thorough and accommodating, Passionate and funny, Makes class fun.  \\

\textbf{Introduction to International Economic Relations}

\textit{Great course and an even better teacher!} \\

\textit{Mr. Storm is clearly passionate about the subject he teaches and works hard to make sure all his students understand the material. His teaching style is very engaging and his tests are challenging. Overall, I feel nearly all of us in his class have learned a lot, and I would recommend him to anyone taking the courses he teaches.} \\

\textit{The instructor did a mid semester eval for himself where as students didn't have to complete if they did not want to. However he clearly read those evals and adjusted his course to meet the students preferred teaching methods, this was very helpful overall.} \\

The topics of trade are interesting and allow for a deeper look into how certain decisions impact a global economy. The teacher is able to show impact of small/large changes of factors. His classes are organized. You are doing a great job!

Interesting real world applications and current events. The instructor prepares clear lectures with a logical flow, very easy to follow. 

\textbf{Economics of Personal Finance}

Eduard brought a great and positive energy to the classroom with each lesson. He made learning about personal finance inviting and not-boring. I'd take his class again if given the opportunity  \\

Professor Storm was very helpful and would be willing to explain materials even after class.  \\

I like applications of the things taught to my financial status, helping with me my finances for college. The instructor is willing to take the time to explain a topic that confuses a student.  \\

I like how easy it was to understand the given information as well as how relevant it was. The instructor is positive and thorough in explaining.  \\

Thank you so much for putting this course together. It has done a great deal for me. I have been out of school for a while and it was very encouraging to build a foundation for myself again.  \\

I like learning how to create a balance sheet and where check for credit. I can budget and save better now. Instructor is able to describe and keep us interested by making materials relatable. He is patient and describes things patiently when we are confused. 

\textbf{Economic Statistics}









\end{document}