---
name: Nam Nguyen
docname: "Updated: Feb 2022 - Resume"
fontawesome: yes
address: "Milwaukee, Wisconsin"
phone: "+1 414 207 7507"
email: "nam.nguyen.thn@gmail.com"
# www: "namnguyen.github.io"
date: "`r format(Sys.time(), '%B %Y')`"
output: function(...) {source('price_entries.R');vitae:::set_entry_formats(price_entries);vitae::cv_document(..., template = "pricetemplate.tex", citation_package = "biblatex")}
---

```{r setup, include=FALSE}
# To save log files
# rmarkdown::render("resume/nprice_resume.Rmd", clean = FALSE)

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

library(tidyverse)
library(vitae)
library(lubridate)
library(glue)
library(rlang)
```

```{r loadData}

# Education
education <- data.table::fread("../data/education.csv",
                               encoding = "UTF-8") %>%
  as_tibble() %>%
  mutate(
    begin = as.Date(begin, format = "%m/%d/%y"),
    end = as.Date(end, format = "%m/%d/%y")
  )

# Job titles
job.titles <- data.table::fread("../data/job-titles.csv",
                                encoding = "UTF-8") %>%
  as_tibble() %>%
  mutate(
    begin = as.Date(begin, format = "%m/%d/%y"),
    end = as.Date(end, format = "%m/%d/%y")
  )

# Skills
skills <- data.table::fread("../data/skills.csv",
                            encoding = "UTF-8") %>%
  as_tibble()

# Job descriptions
job.descriptions <-
  data.table::fread("../data/job-descriptions.csv",
                    encoding = "UTF-8") %>%
  as_tibble()

# Awards
awards <- data.table::fread("../data/awards.csv",
                            encoding = "UTF-8") %>%
  as_tibble()

# Teaching
teaching <- data.table::fread("../data/teaching.csv",
                            encoding = "UTF-8") %>%
  as_tibble()

```

# Education
```{r education, results = "asis"}

education %>%
  arrange(desc(end), begin) %>%
  mutate(what = degree,
         when = year(end),
         with = university,
         where = glue("{city}, {region}, {country}")) %>% 
  select(what, when, with, where) %>% 
  arrange(desc(when)) %>% 
  detailed_entries(
    what,
    when,
    with,
    where,
    .protect = F
  )

```

# Research Interests
**Primary:**   Applied Macroeconomics $\bullet$ Housing and Financial Markets $\bullet$ Forecasting

**Secondary:** Bayesian Econometrics $\bullet$ Unobserved Component models $\bullet$ Optimization

&nbsp;

# Data Science Skills

**Statistics:** machine learning $\bullet$ neural network $\bullet$ Bayesian inference $\bullet$ quantitative methods $\bullet$ panel data analysis $\bullet$ time series models $\bullet$ cross-validation $\bullet$ uncertainty quantification

**Programming Languages:** R $\bullet$ Python $\bullet$ SQL $\bullet$ Matlab $\bullet$ C++ $\bullet$ Stata $\bullet$ SAS

**Software Development:** source control (Git)

**Numerical Methods:** optimization (stochastic, multi-start) $\bullet$ differential equations

**Communication:** presentations $\bullet$ data analysis reports (Rmarkdown, Jupyter) $\bullet$ data visualization (ggplot2)

<!-- ```{r} -->
<!-- skills_formatted <- skills %>% -->
<!--   mutate(skill = if_else(is.na(details)|details=="", glue("{skill}"), glue("{skill} ({details})"))) %>% -->
<!--   group_by(group) %>% -->
<!--   summarize(skills = glue_collapse(skill, sep = " $\\bullet$ ")) -->
<!-- ``` -->

<!-- ```{r, results='asis', width = 40000} -->
<!-- for (group in skills_formatted$group) { -->
<!--   cat( -->
<!--     glue("\\textbf{<<tools::toTitleCase(group)>>}:", .open = "<<", .close = ">>"), -->
<!--     filter(skills_formatted, group == !!group)$skills, -->
<!--     "\n\n\n" -->
<!--   ) -->
<!-- } -->
<!-- ``` -->

&nbsp;

# Experience

```{r experience}
job.titles %>% 
  # Only 5 most recent jobs
  arrange(desc(begin)) %>% 
  filter(year(begin) >= 2010) %>%
  # Join job descriptions
  left_join(job.descriptions) %>% 
  # Arrange by descending begin date
  arrange(desc(begin), descId) %>% 
  # Format as detailed entries
  detailed_entries(
    what = position,
    when = as.character(
      glue("{month(begin, label = TRUE, abbr = TRUE)} {year(begin)} - 
           {if_else(!is.na(end), 
           paste(month(end, label = TRUE, abbr = TRUE), year(end)), 'present')}")),
    with = employer,
    where = glue("{city}, {region}, {country}"),
    why = accomplishments)
```


# Research

<!-- \faicon{book} `r bibliography_entries("publications.bib") %>% filter(type == "chapter") %>% summarize(N = n()) %>% pull(N)` book chapters -->

<!-- \faicon{file-text} `r bibliography_entries("publications.bib") %>% filter(type == "article-journal") %>% summarize(N = n()) %>% pull(N)` peer-reviewed journal publications -->

<!-- \faicon{pencil} `r bibliography_entries("publications.bib") %>% filter(type == "paper-conference") %>% summarize(N = n()) %>% pull(N)` thesis papers -->

<!-- \faicon{pencil} `r bibliography_entries("publications.bib") %>% summarize(N = n()) %>% pull(N)` thesis papers -->
<!-- \faicon{floppy-o} `r bibliography_entries("publications.bib") %>% filter(id %in% c("price_radsets_2019", "price_tvdiff_2019", "price_huntfishapp_2019")) %>% summarize(N = n()) %>% pull(N)` open-source software packages -->

<!-- Full List Available on Google Scholar: https://scholar.google.com/citations?hl=en&user=rXaKU0EAAAAJ -->

<!-- ## Open Source Software -->

<!-- ```{r} -->
<!-- bibliography_entries("publications.bib") %>% -->
<!--   filter(id %in% c("price_radsets_2019", "price_tvdiff_2019", "price_huntfishapp_2019")) -->
<!-- ``` -->
## Working Papers
```{r}
bibliography_entries("publications.bib") %>%
  filter(
    id %in% c(
      "nguyen_house_2021",
      "kishor_measuring_2022",
      "nguyen_identifying_2022"
    )
  ) %>%
  arrange(desc(issued))
```

&nbsp;

# Teaching Experience

**Instructor:** Principles of Macroeconomics x6 $\bullet$ Principles of Microeconomics x2 $\bullet$  Introduction to Economics

**Teaching Assistant:** Intermediate Microeconomics $\bullet$ Principles of Macroeconomics x3 $\bullet$ Principles of Microeconomics x3

&nbsp;

# Memberships
American Economic Association

Midwest Economic Association

National Association for Business Economics

&nbsp;

# Awards and Honors
```{r award}
awards %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

# References

Provided upon request


<!-- \fancyfoot[LO,LE]{\footnotesize This resume was generated on `r Sys.time()` using vitae R package and custom LaTeX template (\href{https://github.com/natbprice/cv}{github.com/natbprice/cv})} -->